Cosmic Microwave Background Power Spectra from Few Bit Timestreams

### 2018-08-13 digitisation.tex
Figures
Added some reliminary figures.

\usepackage[table,usenames,dvipsnames]{xcolor}
%\usepackage{amsmath}
%\usepackage{subfigure}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage{natbib}
%\usepackage{natbib}
\bibliographystyle{fapj}
%\usepackage{graphicx}
%\usepackage{multirow}
\usepackage{soul}

@@

\begin{table}[tbh] % transpose and include hpp!
\begin{center}
\caption{\label{tab:modelparams} Assumed Survey Parameters}
\small
\begin{tabular}{l c c c c}
$\mathrm{NSIDE}$ & $f_{\mathrm{readout}} [\mathrm{Hz}]$ & $f_{{\mathrm{sky}}}$ & $\sigma^{\mathrm{T}}_{\mathrm{det}} [\mathrm{\mu K \sqrt{s}}]$ & $\sigma^{\mathrm{Pol}}_{\mathrm{det}} [\mathrm{\mu K \sqrt{s}}]$\\
\hline
$4096$ & $200$ & $\sim 0.014$ & $500$ & $\sqrt{2}\times500$\\

\end{tabular}
\tablecomments{ 
Parameters used in the simulated observation. The RA speed is tweaked to match the desired hpp.
} \normalsize
\end{center}
\end{table}

@@

we close the normalisation window the first instance the above condition is met. The normalisation constants for each digitisation scheme and channel obtained through this way are then applied to all lower hpp simulations.

@@

Before analysing $C_l^X/C_l^N$ we rebin the power spectra to $\Delta l = 123$. This guarantees that the points in the noise tail are independent of one another, allowing us to extract an uncertainty for the above quantity.

%plot these X/N ?

The results for the 1, 2 and 3 bit digitisation schemes are summarised in figure \ref{fig:extranoise}. We would like to point out three key results. Firstly, 3 Bit digitisation performs the best, followed by 2 Bit and finally 1 Bit digitisation. This is what we expect, given that with each additional bit we retain more information. Secondly, for a fixed detector noise level, the additional percentage to the map noise level due to digitisation is independent of the number of hpp. The added noise therefore scales in the same fashion as the map noise level with the number of hpp, given a fixed detector noise level. Lastly, the added noise levels are astonishingly low. Keeping in mind that CMB detector sensitivity improves in steps of order of magnitude every few years adding an extra percent-level noise term does not deteriorate the results appreciably. This is impressive, given that the use of an optimal 3 bit digitisation scheme will save approximately an order of magnitude in TOD volume.

@@

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip]{Plots/addednoise.png}
  \caption[Current ]{
  Addition to the map noise level due to digitisation. 
           \label{fig:extranoise}
  }
\end{figure*}

\begin{table*}[tbh]
\begin{center}
\caption{\label{tab:experiments} Assumed survey parameters}
\small
\begin{tabular}{l || c c c c c }
Experiment & Sky coverage & Polarized Noise level  & 1/$f$ knee & Beam FWHM \\
& &($\mu$K-arcmin)&&(arcmin.)\\
\hline
\tiny \\ \small
CMB Stage III & & & & \\
~~~~~SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
~~~~~Simons Array & 36\% & 9.5 & 200 & 3.5 \\ 
\tiny \\ \small
%\hline
CMB Stage IV & 55\% & 1.3 & 100 & 4.0 \\
\end{tabular}
\tablecomments{ 
Key numbers about the planned stage III and IV experiments. 
The sky coverage percentages are after galactic cuts. 
Unless otherwise noted,  the Fisher matrix forecasts in this work use these numbers. 
All forecasts also allow for beam and calibration uncertainties as noted in the text. 
} \normalsize
\end{center}
\end{table*}

>>>>

\usepackage[table,usenames,dvipsnames]{xcolor}
%\usepackage{amsmath}
%\usepackage{subfigure}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage{natbib}
%\usepackage{natbib}
\bibliographystyle{fapj}
%\usepackage{graphicx}
\usepackage{multirow}
\usepackage{soul}

@@

\begin{table}[tbh] % transpose and include hpp!
\begin{center}
\caption{\label{tab:modelparams} Assumed Survey Parameters}
\small
\begin{tabular}{l | c}
Parameter & Value\\
\hline
$\mathrm{NSIDE}$ &$4096$\\
$f_{\mathrm{readout}} [\mathrm{Hz}]$ &$200$\\
$f_{{\mathrm{sky}}}$ & $\sim 0.014$\\
$\sigma^{\mathrm{T}}_{\mathrm{det}} [\mathrm{\mu K \sqrt{s}}]$ &$500$\\
$\sigma^{\mathrm{Pol}}_{\mathrm{det}} [\mathrm{\mu K \sqrt{s}}]$ & $\sqrt{2}\times500$\\
\multirow{2}{*}{$\mathrm{hpp}$} & $\left(1, 10, 100 \right) \times 800$\\
& $\left( 1, 10, 100 \right) \times 1024000$ \\
\end{tabular}
\tablecomments{ 
Parameters used in the simulated observation. The RA speed is adjusted to match the desired hpp.
} \normalsize
\end{center}
\end{table}

@@

we close the normalisation window the first instance the above condition is met. The normalisation constants for each digitisation scheme and channel obtained through this way are then applied to all lower hpp simulations. A sample of the obtained power spectra are shown in figures \ref{fig:ttzoom}, \ref{fig:eezoom}, and \ref{fig:bbzoom}.

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/ttzoom.png}
  \caption[Current ]{
  $\mathrm{TT}$ power spectrum reconstructed from a $\sim 10^8\mathrm{hpp}$ map.
           \label{fig:ttzoom}
  }
\end{figure}

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/eezoom.png}
  \caption[Current ]{
  $\mathrm{EE}$ power spectrum reconstructed from a $\sim 10^8\mathrm{hpp}$ map.
\label{fig:eezoom}
}
\end{figure}

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/bbzoom.png}
  \caption[Current ]{
  $\mathrm{BB}$ power spectrum reconstructed from a $\sim 10^8\mathrm{hpp}$ map.
\label{fig:bbzoom}
}
\end{figure}

@@

Before analysing $C_l^X/C_l^N$ we rebin the power spectra to $\Delta l = 123$. This guarantees that the points in the noise tail are independent of one another, allowing us to extract an uncertainty for the above quantity. Plots for $C_l^X/C_l^N$ are shown in figures \ref{fig:clxclntt}, \ref{fig:clxclnee}, and \ref{fig:clxclnbb} for $TT$, $EE$, and $BB$ respectively.

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/ttratio.png}
  \caption[Current ]{
  Calculated ratio of $C_l^X/C_l^N$ of the rebinned $\mathrm{TT}$ power spectrum. The vertical black line indicates from which point onwards data is used in calculating the equivalent noise level.
           \label{fig:clxclntt}
  }
\end{figure}

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/eeratio.png}
  \caption[Current ]{
  Calculated ratio of $C_l^X/C_l^N$ of the rebinned $\mathrm{EE}$ power spectrum.
\label{fig:clxclnee}
}
\end{figure}

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/bbratio.png}
  \caption[Current ]{
  Calculated ratio of $C_l^X/C_l^N$ of the rebinned $\mathrm{BB}$ power spectrum.
\label{fig:clxclnbb}
}
\end{figure}

The deduced additional noise for 1, 2 and 3 bit digitisation schemes are shown with respect to the hits per pixel in the maps in figure \ref{fig:extranoise}. We would like to point out three key results. Firstly, 3 Bit digitisation performs the best, followed by 2 Bit and finally 1 Bit digitisation. This is what we expect, given that with each additional bit we retain more information. Secondly, for a fixed detector noise level, the additional percentage to the map noise level due to digitisation is independent of the number of hpp. The added noise therefore scales in the same fashion as the map noise level with the number of hpp, given a fixed detector noise level. Lastly, the added noise levels are astonishingly low. Keeping in mind that CMB detector sensitivity improves in steps of order of magnitude every few years adding an extra percent-level noise term does not deteriorate the results appreciably. This is impressive, given that the use of an optimal 3 bit digitisation scheme will save approximately an order of magnitude in TOD volume.

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/addednoise.png}
  \caption[Current ]{
  Addition to the map noise level due to digitisation. 
           \label{fig:extranoise}
  }
\end{figure}

@@

%\begin{table*}[tbh]
%\begin{center}
%\caption{\label{tab:experiments} Assumed survey parameters}
%\small
%\begin{tabular}{l || c c c c c }
%Experiment & Sky coverage & Polarized Noise level  & 1/$f$ knee & Beam FWHM \\
%& &($\mu$K-arcmin)&&(arcmin.)\\
%\hline
%\tiny \\ \small
%CMB Stage III & & & & \\
%~~~~~SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
%~~~~~Simons Array & 36\% & 9.5 & 200 & 3.5 \\ 
%\tiny \\ \small
%\hline
%CMB Stage IV & 55\% & 1.3 & 100 & 4.0 \\
%\end{tabular}
%\tablecomments{ 
%Key numbers about the planned stage III and IV experiments. 
%The sky coverage percentages are after galactic cuts. 
%Unless otherwise noted,  the Fisher matrix forecasts in this work use these numbers. 
%All forecasts also allow for beam and calibration uncertainties as noted in the text. 
%} \normalsize
%\end{center}
%\end{table*}
